Unicode Implementation Issues \thanks { This is a working document for the Rexx Language Association (RexxLA). There will be one or more separate requirements documents. It is written in \LaTeX\ \fmtversion\ and was rendered \today\ using \enginedetails. }

### 2024-04-12 ARB/standards/work-in-progress/document/tex/standard/built-in_functions.tex
add filenames

/* Backslash is avoided as some systems don't handle that negation sign.
\emph{/ if argQ)\textgreater3 then returm numeric digits 18 if
arg(1,`E') then if pos(translate(left(arg(1),1)),``CEHLMNRS'')=0 then
return /} (The standard would also allow `O' but what this code is
running on would not.) \emph{/ if arg(3,`E') then if
pos(translate(left(arg(3),1)),``CHLMNS'')=0 then return /} Tf the third
argument is given then the second is mandatory. \emph{/ if arg(3,`E') \&
arg(2,`E')=0 then returm /} Default the first argument. \emph{/ if
arg(1,`E') then Option = translate(left(arg(1),1)) else Option = `N'' /}
Tf there is no second argument, the current time is returned. \emph{/ if
arg(2,`E') = 0 then if arg(1,`E') then return ``TIME'(arg(1)) else
return `TIME'() /} One cannot convert to elapsed times. */ if
pos(Option, `ERO') \textgreater{} 0 then returm InValue = arg(2) if
arg(3,`E') then InOption = arg(3) else InOption = `N' HH =0 MM = 0 SS =0
HourAdjust = 0 select

@@

when InOption == `L'' \textbar{} InOption == `N' then parse var InValue
HH `:' MM `:' SS when InOption == `M' then MM = InValue otherwise SS =
InValue end if datatype(HH,`W')=0 \textbar{} datatype(MM,`W')=0
\textbar{} datatype(SS,`N')=0 then returm HH = HH + HourAdjust /*
Convert to microseconds \emph{/ Micro = trunc((((HH } 60) + MM) * 60 +
SS) * 1000000) /* There is no special message for time-out-of-range; the
bad-format message is used. \emph{/ if Micro\textless0O \textbar{} Micro
\textgreater{} 24}3600* 1000000 then returm /* Reconvert to further
check the original. */ if TimeFormat(Micro,InOption) == InValue then
return TimeFormat(Micro, Option) return

@@

String = \#Bif Arg.1 Num = \#Bif\_ Arg.2 if \#Bif\_ArgExists.3 then
Length = \#Bif Arg.3 else Length = max(length (String) +1-Num, 0) if
\#Bif\_ArgExists.4 then Pad = \#Bif\_ Arg.4 else Pad = ' `! Output =''
do Length \#Response Config Substr(String,Num) /* Attempt to fetch
character.*/ Character \#Outcome

>>>>

/* Backslash is avoided as some systems don't handle that negation sign.
\emph{/ if argQ)\textgreater3 then returm numeric digits 18 if
arg(1,`E') then if pos(translate(left(arg(1),1)),``CEHLMNRS'')=0 then
return /} (The standard would also allow `O' but what this code is
running on would not.) \emph{/ if arg(3,`E') then if
pos(translate(left(arg(3),1)),``CHLMNS'')=0 then return /} Tf the third
argument is given then the second is mandatory. \emph{/ if arg(3,`E') \&
arg(2,`E')=0 then returm /} Default the first argument. \emph{/ if
arg(1,`E') then Option = translate(left(arg(1),1)) else Option = `N'\,'
/} Tf there is no second argument, the current time is returned. \emph{/
if arg(2,`E') = 0 then if arg(1,`E') then return ``TIME'(arg(1)) else
return `TIME'() /} One cannot convert to elapsed times. */ if
pos(Option, `ERO') \textgreater{} 0 then returm InValue = arg(2) if
arg(3,`E') then InOption = arg(3) else InOption = `N' HH =0 MM = 0 SS =0
HourAdjust = 0 select

@@

when InOption == `L'\,' \textbar{} InOption == `N' then parse var
InValue HH `:' MM `:' SS when InOption == `M' then MM = InValue
otherwise SS = InValue end if datatype(HH,`W')=0 \textbar{}
datatype(MM,`W')=0 \textbar{} datatype(SS,`N')=0 then returm HH = HH +
HourAdjust /* Convert to microseconds \emph{/ Micro = trunc((((HH } 60)
+ MM) * 60 + SS) * 1000000) /* There is no special message for
time-out-of-range; the bad-format message is used. \emph{/ if
Micro\textless0O \textbar{} Micro \textgreater{} 24}3600* 1000000 then
returm /* Reconvert to further check the original. */ if
TimeFormat(Micro,InOption) == InValue then return TimeFormat(Micro,
Option) return

@@

String = \#Bif Arg.1 Num = \#Bif\_ Arg.2 if \#Bif\_ArgExists.3 then
Length = \#Bif Arg.3 else Length = max(length (String) +1-Num, 0) if
\#Bif\_ArgExists.4 then Pad = \#Bif\_ Arg.4 else Pad = ' `! Output ='\,'
do Length \#Response Config Substr(String,Num) /* Attempt to fetch
character.*/ Character \#Outcome
